\section{2 Players Protocol}
In ~\cite{BFS86}, Babai, Frankl and Simon prove the following for two players:
\begin{theorem}
For all product distributions $\mu$, 
\begin{equation*}
    D^{\mu}(\text{DISJ}_n) \in O(\sqrt{n}\log{n})
\end{equation*}
\end{theorem}
They presented a protocol that maintains a universe set $U$ where $\bigcup_{i=1}^k X_i \subseteq U$ throughout the protocol. \newline
The protocol operates in iterations where in every iteration it reduces the universe's size. \newline
The fact that the input's distribution is a product distribution is used in the part it reduces the universe's size.
Every iteration operates as follows: \newline
\begin{enumerate}
    \item If Alice or Bob has a small input, calculate the precise solution and halt.
    \item Bob calculate the probability for disjointness in the current universe over Alice's input distribution (Bob knows his own input).
    \item If the probability is small, guess "Intersecting".
    \item Otherwise, Bob finds in the public randomness a sample of Alice's input which is disjoint to his and sends the index of the sample to Alice.
    \item They both reduce the universe by the sample set (which is disjoint to Bob's input).
\end{enumerate}
In this protocol there are few important points. It depends strongly on the independence of the inputs where firstly Bob can calculate the probability for disjointness given its input and secondly both of them can sample Alice's input using the public randomness. Moreover, the index of the sample is short since the probability for disjointness isn't insignificant. \newline
This protocol is not easily extended to multiplayer settings since in multiplayer, we need somehow choose who talks and which event's probability is used. \newline
In the following paper, I tried to solve this issue using a sequential point of view for the disjointness problem.
