\section{Sequential Point of View}
\label{sec:seq_disj}

Consider a process where we start with some universe $U$ (where $\bigcap_{i = 1}^k x_i \subseteq U$),
and gradually intersect it with more and more players' inputs, 
obtaining a sequence of sets
\begin{equation*}
    \bigcap_{j = 1}^k x_j = U \cap \bigcap_{j = 1}^k x_j \subseteq  U \cap \bigcap_{j = 1}^{k-1} x_j \subseteq \ldots \subseteq  U \cap x_1 \cap x_2 \subseteq  U \cap x_1 \subseteq U
\end{equation*}
Let us denote these sets $A_i(U) = U \cap (\bigcap_{j \leq i} x_j)$ (and in particular, $A_0(U) = U$).
\begin{equation*}
    \bigcap_{j = 1}^k x_j = A_k(U) \subseteq A_{k-1}(U) \subseteq \ldots \subseteq A_1(U) \subseteq A_0(U) = U
\end{equation*}

We omit the universe $U$ from our notation when it is clear from the context. \newline
Pay attention that any element that is missing from some $A_i$ is definitely not in the intersection.
Our goal is to try to find two consecutive sets $A_i, A_{i+1}$ such that $A_{i+1}$ is \emph{significantly smaller} than $A_i$,
and then use this fact to eliminate many elements from consideration, reducing the universe size.

\begin{definition}
  With respect to a universe $U \subseteq [N]$ of size $n = |U| > 0$ and inputs $x_1,\ldots,x_k \subseteq [N]$,
  we say that an index $i \in [k]$ is \emph{good} if
  \begin{enumerate}
    \item $|A_i(U)| / |A_{i-1}(U)| < 1/n^{1/k}$, and
    \item $|A_{i-1}(U)| \geq n^{1-(i-1)/k}$.
  \end{enumerate}
  \label{def:good}
\end{definition}

\begin{lemma}
  Fix a universe $U \subseteq [N]$ of size $|U| = n > 0$ and inputs $x_1,\ldots,x_k \subseteq [N]$,
  and suppose that $\bigcap_{i = 1}^k x_i = \emptyset$.
  Then there is some good index $i \in [k]$.
  \label{lemma:narrow}
\end{lemma}
\begin{proof}
  We first prove that there is an index $j \in [k]$ that satisfies the first property in Def.~\ref{def:good}, and then we show
  that the minimal such index $j$ also has the second property.

  Let $j \in [k]$ be the maximal index such that 
  \begin{equation*}
    A_{j-1} \neq \emptyset.
  \end{equation*}
  There is such a $j$, because $A_0 = U \neq \emptyset$.

  Observe that $A_{j} = \emptyset$:
  if $j < k$ then this is immediate (otherwise $j$ would not be maximal),
  and
  if $j = k$, then $A_j = A_k = U \cap \bigcap_{i=1}^k x_i = \emptyset$ by assumption.
  Thus,
  \begin{equation*}
    \frac{|A_j|}{|A_{j-1}|} = \frac{0}{|A_{j-1}|} = 0 < \frac{1}{n^{1/k}},
  \end{equation*}
  so we know that (1) holds for $j$.


  Let $j^{\ast}$ denote the minimal index in $[k]$ that satisfies (1).
  Because of its minimality, for all $i \in [j^\ast-1]$ we have
  \begin{equation*}
    \frac{|A_i|}{|A_{i-1}|} \geq \frac{1}{n^{1/k}}.
  \end{equation*}
  Therefore,
  \begin{align*}
    \frac{|A_{j^\ast - 1}|}{|A_0|} = 
    \frac{|A_{j^\ast - 1}|}{|A_{j^\ast-2}|} \cdot \frac{|A_{j^\ast-2}|}{|A_{j^\ast-3}|} \cdot \ldots \cdot \frac{|A_1|}{|A_0|}
    \geq
    \left(  \frac{1}{n^{1/k}} \right)^{j^\ast - 1}
    =
    \frac{1}{n^{\frac{j^\ast - 1}{k}}}.
  \end{align*}
  Since $|A_0| = n$, 
  \begin{align*}
    |A_{j^\ast - 1}| \geq n^{1 - \frac{j^\ast-1}{k}}.
  \end{align*}
\end{proof}

Let $D_i(U)$ be an indicator for the event that $\bigcap_{j = 1}^k x_j = \emptyset$ and in addition $i$ is a good index
with respect to the universe $U$.
The lemma implies that for any $U \subseteq [n]$ and inputs $x_1,\ldots,x_n$ such that $\bigcap_{i = 1}^k x_i \subseteq U$,
we have
$\bigcap_{i = 1}^k x_i = \emptyset$
iff $\bigvee_{i = 1}^k D_i(U) = 1$.
As usual, we omit the universe $U$ from our notation where possible.

\paragraph{Significant players.}
A player $i \in [k]$ does not know whether or not $i$ is good,
as this depends on the inputs of the other players.
However, player $i$ can compute the \emph{probability} that the conditions hold:
define
\begin{equation*}
  \gamma_i = \gamma_i(x_i, U) \coloneq \Pr_{(\rv{X}_{-i}) \sim \mu}\left[ D_i(U) \given \rv{X}_i = x_i \right].
\end{equation*}
We say that player $i$ is \emph{significant} if $\gamma_i \geq \eps / (kN^{1-1/k})$.
